LAs_clusters

### 2020-09-11 src/LAs_Clusters.Rmd
more aux regressions

## Auxiliary regression, dep. var.: upload clusters, without upload variables

```{r upload regression no upload and test, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

@@

aux <- multinom(as.factor(cluster.up) ~ pop16_64 + # how about young population share, pop +
                  pop.dens + job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop), data = data, 
                trace = F) # to avoid messages

@@

stargazer(aux, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c("pop. 16-64, 2018",
                             "pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of dministrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            nrow(data), nrow(data), nrow(data),
                            nrow(data), nrow(data), nrow(data),
                            nrow(data), nrow(data), nrow(data)))))

@@

>>>>

## Auxiliary regression, dep. var.: upload clusters

```{r upload regression , results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

@@

aux <- multinom(cluster.up ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) # non sensitive to addition of other tests pm
                , data = data, 
                trace = F) # to avoid messages

@@

n.obs <- dim(aux$fitted.values)[1]

stargazer(aux, 
          type = "html",
          #type = "text",
          nobs = T,
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs))))

@@

## Auxiliary regression, dep. var.: test clusters

```{r test regression, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

# convert dependent variable to factor
data$cluster.tests <- as.factor(data$cluster.tests)
data$cluster.tests <- relevel(data$cluster.tests, "5") # base category: cluster 5

aux <- multinom(cluster.tests ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) # non sensitive to addition of other tests pm
                , data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.null <- multinom(cluster.tests ~ 1, data = data)
r2 <- 1-logLik(aux)/logLik(aux.null)

n.obs <- dim(aux$fitted.values)[1]

stargazer(aux, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs))))

## Auxiliary regression, dep. var.: down clusters

```{r down regression, results= 'asis', message=F, error=F, warning=F}
# helpful sources: http://www.princeton.edu/~otorres/LogitR101.pdf
# https://thestatsgeek.com/2014/02/08/r-squared-in-logistic-regression/

# convert dependent variable to factor
data$cluster.down <- as.factor(data$cluster.down)
data$cluster.down <- relevel(data$cluster.down, "2") # base category: cluster 2

aux <- multinom(cluster.down ~ 
                  #pop16_64 + # non sign, while pop is
                  pop +
                  #pop.dens + 
                  job.dens2018 + # pop.dens is still insignificant when job.dens is excluded
                  distMet + distLondon + south +
                  managers + tech + skilled + prof + admin + caring + plant +
                  earnings + I(total.busi/pop) +
                  I(LAD.tests.am20/pop) # non sensitive to addition of other tests pm
                , data = data, 
                trace = F) # to avoid messages

# McFadden's R squared
aux.null <- multinom(cluster.down ~ 1, data = data)
r2 <- 1-logLik(aux)/logLik(aux.null)

n.obs <- dim(aux$fitted.values)[1]

stargazer(aux, 
          type = "html",
          #type = "text",
          digits = 3,
          covariate.labels=c(#"pop. 16-64, 2018",
                             "pop, 2018",
                             #"pop. densuty, 2018",
                             "job density, 2018",
                             "distance to nearest met. area",
                             "distance to London",
                             "South of the UK",
                             "% of managerial jobs, 2020",
                             "% of tech jobs, 2020",
                             "% of skilled trade jobs, 2020",
                             "% of professional jobs, 2020",
                             "% of administrative jobs, 2020",
                             "% of leisure jobs, 2020",
                             "% of machine operation jobs, 2020",
                             "earnings, 2019",
                             "n. business est. per hab., 2019",
                             "n. of AM broadband tests per hab., 2019"),
          add.lines = list(c("McFadden's R squared",
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3), round(r2[1],3), round(r2[1],3),
                             round(r2[1],3)),
                           (c("N",
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs, n.obs, n.obs,
                            n.obs))))
